\section{4-1-2013}

%To-Do: get FEKO code from email

\subsection{Loop Antennas}

The first ever designed antenna was the Loop Antenna by Heinrich Hertz in the
19th century.

Loops are classified in terms of their electrical size:
\begin{enumerate}
  \item small circumference $< \frac{\lambda}{10}$
  \item large circumference
\end{enumerate}

    45 foot loop for a full-wavelength antenna! Doable, but not readily
    mountable\ldots

    Typically used as:
      -Rx antennas for portable radios and pagers
      -Loops have small signal to noise ratio, but are not very efficient
      -Used for radio wave navigation, direction finding
      -Probes for near-field measurements
      -Probes for waveguide excitation
      -Short range wireles communications
      -Short range wireless power
        --pacemakers, for example
      -Ground penetration at very low freqs (water on Mars
      -Parts of other antennas
        --Yagi-Uda directional arrays
        --Helical

Radiation Resistance is very small, and this is a major problem. In contrast to
dipoles:
\[ l \leq \frac{\lambda}{10}\]

Loop antenna radiation resistance is VERY SMALL (power of 4 as opposed to power
of 2)

\[
  P_{rad} = \eta\cdot \big( \frac{\pi}{12} \big) (ka)^4 |I_0|^2 = 1/2
  |I_0|^2 R_r
  20\pi^2\cdots
\]

\[
  C=0.1\cdot \lambda
  R_{r_{loop}} \approx 0.02\Omega
  R_{r_{dipole}} \approx 2\Omega
  \eta_{loop} = \frac{0.02}{0.12} \approx 16\%
  \eta_{dipole} = \frac{2}{2.1} \approx 95\%
\]

For a small loop
\[
  R_r = 20\pi^2(\frac{C}{\lambda}
  D_0=\frac{3}{2}
  A_{em}={3\lambda^2}{8\pi} %!
\]
2x the width of a spherical (isotropic) antenna.

How can radiation resistance be increased?
  Two practical ways:
  -Increase number of turns
  \[
    R_r \approx 20 \pi^2 \frac{ }
  \]
  -Use ferrite rods: Increases magnetic flux through the loops so that the
  total open circuit voltage of the rx loops ant. is increased!
  %But this is not practical for our design!
How to feed loops? %see powerpoint for sketches!
-two wire loop (TRL)
-coaxial cable (very nice antenna)
-Shielded loop

%See loop paper sent by Filipovic
Tuning the cap changes the reflection coefficient, and therefore ``tunes'' the
radio!
The coupling loop is used to match the impedance (works as a transformer) of the loop (very small) to
the coax cable (50 $\Omega$)
%sketch the donut-like shape of the radiation pattern!

\subsection{Friis}

How much power rx antenna delivers to rxer?
%Everything is in dBm!
%norcal out is 2W, in dBm this is 33dBm -> why?

\subsection{Effects of Surrounding Environment}



